---
title: "RWorksheet_Sumintao#4b"
output: pdf_document
date: "2023-11-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1.for() loop Using the for loop, create an R script that will display a 5x5 matrix as shown in Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

A <- c(1,2,3,4,5)
zero_matrix <- matrix(0, nrow = 5,ncol = 5)
matrix_result <- rbind(A, zero_matrix)
print(matrix_result)


#2. Print the string "*" using for() function. The output should be the same as shown in Figure

for (i in 1:5){
jls <- rep ("*",i)
print(jls)
}
  
#3. Get an input from the user to print the Fibonacci sequence starting from the 1st inputup to 500. Use repeat and break statements. Write the R Scripts and its output.

 a <- b
 b <- nextFib
userInp <- as.numeric(readline("enter a number to start the Fibonacci sequence:"))

a <- 0
b <- 1

cat("Fibonnaci sequence startingfrom", userInp,":")
cat(userInp," ")

repeat {
 nextFib <- a + b
 
  if (nextFib >500) {
    break
    
 cat(nextFib," ")

}






#4.Import the dataset as shown in Figure 1 you have created previously.




#5.The monthly income of Dela Cruz family was spent on the following:

#a.Create a piechart that will include labels in percentage.Add some colors and title of the chart. Write the R scripts and show its output.

```{r}
data <- c(60, 10, 5, 25)
labels <- c("Food", "Electricity", "Savings", "Miscellaneous")
colors <- c("blue", "black", "violet", "red")
pie(data, labels = labels, col = colors, main = "My Pie Chart")
```

#6. Use the iris dataset.

```{r}
data(iris)

species_count <- table(iris$Species)
colors <- c("black", "blue", "violet", "red")
pie(species_count, labels = levels(iris$Species), col = colors, main = "Iris Species Distribution")
```

#a. Check for the structure of the dataset using the str() function. Describe what you have seen in the output.

data(iris)
str(iris)


#b. Create an R object that will contain the mean of the sepal.length, sepal.width,petal.length,and petal.width. What is the R script and its result?





#c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write the R script and its result.

```{r}
data(iris)
species_count <- table(iris$Species)
colors <- c("skyblue", "blue", "black", "red")
pie(species_count, labels = levels(iris$Species), col = colors, main = "Iris Species Distribution")
legend("topright", legend = levels(iris$Species), fill =colors, title = "Species")
```


#d. Subset the species into setosa, versicolor, and virginica. Write the R scripts and show the last six (6) rows of each species.

```{r}
data(iris)
setosa_data <- subset(iris, Species == "setosa")
versicolor_data <- subset(iris, Species == "versicolor")
virginica_data <- subset(iris, Species == "virginica")

tail(setosa_data)
tail(versicolor_data)
tail(virginica_data)
```

#e. Create a scatterplot of the sepal.length and sepal.width using the different species(setosa,versicolor,virginica). Add a title = “Iris Dataset”, subtitle = “Sepal width and length, labels for the x and y axis, the pch symbol and colors should be based on the species.


